AGB Stars in the IR: Physical Characteristics, Galactic Spatial Distribution, and Chemical Impact of the Milky Way AGB Population

### 2015-06-22 paper1/paper1_data.tex
Edited sections 2.2, 2.3, and 2.5

Now rearrange the old text below in these subsections:

\subsection{WISE-2MASS catalog}

\subsection{AGB stars from SIMBAD database}

\subsection{AGB stars from optical time-domain surveys}
A few sentences of introduction...
\subsubsection{MACHO}
\subsubsection{OGLE-III}

@@

\subsection{Merged sample}

How was it merged, which further cuts and why...

>>>>

\subsection{WISE-2MASS catalog}
Write a few sentences about the WISE survey...

\subsection{AGB stars from SIMBAD database}
The SIMBAD database\footnote{\url{http://simbad.u-strasbg.fr/simbad/}} is comprised of basic data, classifications, and measurements for all types of astronomical objects from a variety of surveys.  Classifications are hierarchical, and are classified with increasing specificity based on the available data, though each star can have multiple classifications. AGB stars have subcategories of C-stars ([C/O] $>$ 1) and S-stars ([C/O] $\sim$ 1). Where subclassification is unclear, the main classification remains as AGB star. OH/IR stars are subsets of peculiar stars that specifically show strong OH maser emission and strong IR emission, identifying them clearly as AGB stars.  Mira-type variables are a subset of variable stars, and are classified based upon their periodicity. Semi-regular variables are not included as they contain an unknown mixture of AGB stars and red supergiants. The sample of AGB stars from SIMBAD was obtained by querying all objects with types classified as C-stars (23,628), S-stars (1,514), AGB stars (4,459), OH/IR stars (1,265), and Mira-type variables (10,828). Without duplicate objects between the five types, there is a total of 39,348 AGB stars from SIMBAD.

\subsection{AGB stars from optical time-domain surveys}
Many of the identifications in the SIMBAD catalog are from spectroscopic studies, however many more AGB stars have been found through their characteristic optical periodicity. The \emph{Optical Gravitational Lens Experiment} (OGLE) and the \emph{MAssive Compacy Halo} (MACHO) survey have are two time-domain surveys that have captured and catalogued such variability.

\subsubsection{MACHO}

\subsubsection{OGLE-III}

@@

\subsection{Merged sample}
Each AGB sample as well as the SDSS sources were matched separately to the ALLWISE data products via the {\tt GATOR} tool at the NASA/IPAC Infrared Science Archive\footnote{\url{http://irsa.ipac.caltech.edu/cgi-bin/Gator/nph-scan?mission=irsa&submit=Select&projshort=WISE}}. The accepted matching radius was 3". The matched sample was further reduced by enforcing the WISE 5$\sigma$ faint limits of [$W1/W2/W3/W4$] $<$ [$16.83/15.6/11.32/8.0$], saturation limits of [$W1/W2/W3/W4$] $>$ [2.0/1.5/-3.0/-4.0], signal-to-noise ratios greater than 3 in each WISE band. We constrain the possibility for a mismatched extragalactic IR source by asserting that the extended source flag $\le$ 1, corresponding either to a point source (flag = 0) or a source whose profile-fit photometry is goodness-of-fit is $>$ 3 in any WISE band but is not coincident with any extended sources from the 2MASS survey. We also require only one match to a 2MASS source within 3".

{\color{red}{How was it merged, which further cuts and why...}}
